### 2014-05-13 paper/main.tex
Fix

    \item[Стохастичність.] Для всіх \(v \in V\)
    \[ \xi_v = \{\xi^t_v\ |\ t = 0, 1, \ldots \}\] 
    \[ (\Omega, \mathcal{F}, P).\quad \xi_v^t : X_v \rightarrow [0, 1]\ ,\]
    де \( \xi_v \) – стохастичний процес, що визначає стан \(v\) у кожен момент часу \(t\). 
    \label{stochasticprocess}

>>>>

    \item[Стохастичність.] Для всіх \(v \in V\)
    \[ \xi_v = \{\xi^t_v\ |\ t = 0, 1, \ldots \}\] 
    \[ (\Omega, \mathcal{F}, P).\quad \xi_v^t : \Omega \rightarrow X_v\ ,\]
    де \( \xi_v \) – стохастичний процес, що визначає стан \(v\) у кожен момент часу \(t\). 
    \label{stochasticprocess}
